iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-24 manuscript/main.tex
fixed equal contribution plus corresponding author symbols
IMBEI as acronym added

\title{iSEE: Interactive SummarizedExperiment Explorer}
\titlenote{The title should be detailed enough for someone to know whether the article would be of interest to them, but also concise. Please ensure the broadness and claims within the title are appropriate to the content of the article itself.}
\author[1]{Kevin Rue-Albrecht}
\author[2,3]{Federico Marini}
\author[4]{Charlotte Soneson}
\author[5]{Aaron T. L. Lun}

\affil[1]{Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom}
\affil[2]{Center for Thrombosis and Hemostasis (CTH), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[3]{Institute for Medical Biostatistics, Epidemiology and Informatics, University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[4]{University of Zurich and SIB Swiss Institute of Bioinformatics, Zurich, Switzerland}
\affil[5]{Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom}

% TODO: $\dagger$ These authors contributed equally.}
% TODO: symbol for corresponding author e.g. $\ast$

>>>>

\title{iSEE: Interactive SummarizedExperiment Explorer}
\titlenote{The title should be detailed enough for someone to know whether the article would be of interest to them, but also concise. Please ensure the broadness and claims within the title are appropriate to the content of the article itself.}
\author[1,$\dagger$]{Kevin Rue-Albrecht}
\author[2,3,$\dagger$]{Federico Marini}
\author[4,$\dagger$]{Charlotte Soneson}
\author[5,$\dagger$,$\ast$]{Aaron T. L. Lun}

\affil[1]{Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom}
\affil[2]{Center for Thrombosis and Hemostasis (CTH), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[3]{Institute for Medical Biostatistics, Epidemiology and Informatics (IMBEI), University Medical Center of the Johannes Gutenberg University Mainz, Mainz}
\affil[4]{University of Zurich and SIB Swiss Institute of Bioinformatics, Zurich, Switzerland}
\affil[5]{Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom}
\affil[$\dagger$]{These authors contributed equally.}
\affil[$\ast$]{To whom correspondence should be addressed.}
